---
title: "Div I Project"
author: "Elina Gordon-Halpern"
date: "February 25, 2022"
output: 
  html_document:
    toc: yes
    toc_float: yes
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Metadata

### Purpose

> The purpose of my function is to serve as a budgeting tool. It takes in two inputs: the user's annual salary, estimated to the nearest $1000, and the percent of their income that they would like to contribute to savings, and returns a suggested goal for ideal monthly savings.

### Dependencies/Setup

> Load any packages or other pre-processing steps that are necessary to make your function work in the chunk below. The chunk should be as [parsimonious](https://en.wiktionary.org/wiki/parsimonious) as possible.

```{r load, message=FALSE}
library(tidyverse)
```


### Arguments

> List the arguments your function takes. Specify the data type, default value (if applicable), and any other assumptions you are making about the value of each argument. 

- `x`: a numeric vector representing annual salary, in 1000's of dollars.
- `y`: a numeric vector representing the percent of monthly income that the user would like to contribute to savings.

### Result

> What does your function return? Specify the data type and any other assumptions you are making. 

- a numeric vector representing the ideal monthly savings based on the salary and savings goal represented by the input vectors `x` and `y`. 

## Code

> Paste your code in the chunk below. 

```{r code}
salary_to_savings <- function(x,y) {
 ((x * 1000)/12)/(100/y)

```

## Examples

> Give 2-3 examples of typical usage of your function. Describe in words what is being illustrated.

This demonstrates a simple example of the function, the suggested savings for an annual salary of $75k and a goal of saving 15% of monthly income:

```{r ex1}
salary_to_savings(75, 15)
```

This shows a list of suggestions for annual salaries of $50-100k with the goal of contributing 20% to savings:

```{r}
salary_to_savings(50:100, 20)
```

## Testing

> Provide a few examples of outputs that you expect your function will match, given a specific input. [Best if you use the [`testthat` package](https://github.com/r-lib/testthat).] 

```{r tests, message=FALSE}
salary_to_savings(0,0) ==  ((0 * 1000)/12)/(100/0)
salary_to_savings(70,18) ==  ((70 * 1000)/12)/(100/18)
salary_to_savings(55,22) ==  ((55 * 1000)/12)/(100/22)

# using testthat
library(testthat)
expect_equal(salary_to_savings(0,0),((0 * 1000)/12)/(100/0))
expect_equal(salary_to_savings(70,18),((70 * 1000)/12)/(100/18))
expect_equal(salary_to_savings(55,22),((55 * 1000)/12)/(100/22))

```

